A Detection of the Environmental Dependence of the Stellar Halos of Massive Central Galaxies

### 2017-01-23 draft/ms_v3.tex
test
Update

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL

@@

%\title{The Environment and Structure of Massive Central Galaxies
%       using the Subaru Hyper Suprime-Cam Survey}

%\title{Environmental Dependence of the Structures of Massive Central 
%       Galaxies at $0.3 < z < 0.5$}

@@

@@

    \update{
    In the past decade, the mass assembly history and structural evolution of massive 
    ETGs remain an active topic.  
    More convincing evidence from observations of massive galaxies at high redshift 
    suggest that the progenitors of massive elliptical galaxies today are quite different 
    in structural properties (e.g. \citealt{Bezanson2009}, \citealt{vanDokkum2010}).  
    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor 
    of 2 to 4 (e.g. \citealt{Newman2012}, \citealt{vdWel2014}), perhaps decrease the 
    central stellar velocity dispersion a little (e.g. \citealt{vandeSande2011}, 
    \citealt{Belli2014}) without changing their inner \mden{} profiles too much 
    (e.g. \citealt{Szomoru2012}, \citealt{Patel2013}) and  in the last 8-10 Gyrs.  
    With the help from better simulations, the promising ``two-phase'' formation 
    scenario seems to be able to deal with these challenges well (e.g. 
    \citealt{Oser2010}, \citealt{Oser2012}).
    However, it raises additional questions.
    As the massive central galaxies in more massive halos should have different mass 
    assembly history, experience more (minor) mergers than the ones in smaller halos, 
    we expect to see certain structural properties depend on ``environment''. 
    Interestingly, although hints of such dependence have been noticed at high redshift 
    (e.g. \citealt{Papovich2012}, \citealt{Delaye2014}), no clear evidence has been found 
    at low redshift (e.g. \citealt{Nair2010}, \citealt{HCompany13}). 
    }

    \plan{Basic idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey\ldots}
    \end{itemize}

    \update{Here, we take advantage of the excellent image quality of the HSC survey, and 
    investigate the potential environmental dependence of structure for massive galaxies 
    vial comparing the surface \mstar{} density profiles and structural scaling relations 
    between massive central galaxies in different environments. 
    As shown in Fig.\ref{fig:sdss_compare}, the HSC $i$-band images are typically 3-4 
    magnitude deeper than SDSS ones, and have much better seeing condition 
    (median FWHM$\sim 0.6^{\arcsec}$), hence they are perfect for mapping the \mstar{}
    distributions of massive galaxies out to very large radius. 
    With the help of a cluster catalog, we select a large sample of massive central 
    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.}

    \update{Due to the difficulty in appropriately modeling the \mstar{} distributions of 
    massive galaxies out to their very outskirts, we focus on \mstar{} within two different 
    physical apertures in this work:}

    \begin{itemize}
        \item \update{\mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
            helps reveal interesting environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.}
        \item \update{\mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.}
    \end{itemize}

    \update{Massive central galaxies in this work show an intriguing diversity on the 
    plane defined by these two metrics.  
    We preview this using Fig.\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
    a large range of outer structures. 
    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
    component, it is of great interest to investigate the relation between their 
    environments and outer envelopes that are assembled at later time. 
    It is worth noting that, although a circular aperture is shown on 
    Fig.\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
    average isophotal shape for photometry in this work.}
    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
    significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

@@

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\lambda}=0.7$. 
%% ------------------------------------------------------------------------------------ %%

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL

@@

@@

    Massive galaxies are important cosmic probes and unique laboratories to study the 
    theory of galaxy formation and evolution. 
    In the nearby universe, massive galaxies are dominated by early-type, quiescent 
    galaxies (\addref{}). 
    Under the $\Lambda$-CDM cosmology, they are the end products of the hierarchical
    structural growth along with their host dark matter halos (\addref{})
    They should start to form very early on in the highest peaks of density field 
    (\addref{}), and are very likely the descendants of the extreme star-forming galaxies
    (e.g. sub-millimeter galaxies, \addref{}) and luminous QSOs (\addref{}) detected at 
    very high redshift. 
    Nowadays, the hierarchical growth scenario under the $\Lambda$-CDM cosmology can 
    already predict important statistical properties of galaxies that are in reasonable
    consistent with observations, like the stellar mass-halo mass relation 
    (SMHM, e.g. \addref{}) and the stellar mass function (SMF, e.g. \addref{}) 
    at different redshift. 
    However, these statistics still have large uncertainties and potential problems at 
    the high mass end (e.g. \addref{}) that reflect limitations in both theoretical and 
    observational sides. 
    Therefore, it is fundamentally important for us to understand the star formation, mass 
    assembly, and structural evolution history of these massive galaxies.

    Thanks to the advances in observations at higher redshift and numerical simulation 
    with more realistic physics, we now realize that these massive, early-type galaxies 
    must have experienced dramatic structural and dynamical transformation in the last 
    $\sim$ 10 Gyrs.
    More and more convincing observations at high redshift point out that the 
    progenitors of $z=0$ massive elliptical galaxies today are quite different 
    in structural properties (e.g. \citealt{Bezanson2009}, \citealt{vanDokkum2010}).  
    Collectively, they need to increase their ``size'' ($R_{\mathrm{e}}$) by a factor 
    of 2 to 4 (e.g. \citealt{Newman2012}, \citealt{vdWel2014}), perhaps decrease the 
    central stellar velocity dispersion a little (e.g. \citealt{vandeSande2011}, 
    \citealt{Belli2014}) without changing their inner \mden{} profiles too much 
    (e.g. \citealt{Szomoru2012}, \citealt{Patel2013}) and  in the last 8-10 Gyrs.  
    With the help from better simulations, the promising ``two-phase'' formation 
    scenario seems to be able to deal with these challenges well (e.g. 
    \citealt{Oser2010}, \citealt{Oser2012}).
    However, it raises additional questions.
    As the massive central galaxies in more massive halos should have different mass 
    assembly history, experience more (minor) mergers than the ones in smaller halos, 
    we expect to see certain structural properties depend on ``environment''. 
    Interestingly, although hints of such dependence have been noticed at high redshift 
    (e.g. \citealt{Papovich2012}, \citealt{Delaye2014}), no clear evidence has been found 
    at low redshift (e.g. \citealt{Nair2010}, \citealt{HCompany13}).

@@

    Here, we take advantage of the excellent image quality of the HSC survey, and 
    investigate the potential environmental dependence of structure for massive galaxies 
    vial comparing the surface \mstar{} density profiles and structural scaling relations 
    between massive central galaxies in different environments. 
    As shown in Fig.\ref{fig:sdss_compare}, the HSC $i$-band images are typically 3-4 
    magnitude deeper than SDSS ones, and have much better seeing condition 
    (median FWHM$\sim 0.6^{\arcsec}$), hence they are perfect for mapping the \mstar{}
    distributions of massive galaxies out to very large radius. 
    With the help of a cluster catalog, we select a large sample of massive central 
    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.

    Due to the difficulty in appropriately modeling the \mstar{} distributions of 
    massive galaxies out to their very outskirts, we focus on \mstar{} within two different 
    physical apertures in this work:

    \begin{itemize}
        \item \mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
            helps reveal interesting environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.
        \item \mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.
    \end{itemize}

    Massive central galaxies in this work show an intriguing diversity on the 
    plane defined by these two metrics.  
    We preview this using Fig.\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
    a large range of outer structures. 
    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
    component, it is of great interest to investigate the relation between their 
    environments and outer envelopes that are assembled at later time. 
    It is worth noting that, although a circular aperture is shown on 
    Fig.\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
    average isophotal shape for photometry in this work.
    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
    significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

@@

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\lambda}=0.7$.
